A Study of the Usage of Eval in R

### 2020-08-21 inst/paper/main.tex
minor

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{xspace}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\newcommand{\missingNumber}{\textcolor{red}{XX}\xspace}
\newcommand{\missingPercentage}{\textcolor{red}{XX\%}\xspace}
\newcommand{\missingTable}{\textcolor{red}{XXTable}\xspace}
\newcommand{\missingGraph}{\textcolor{red}{XXGraph}\xspace}
\begin{document}

\title{On the Design, Use and Removal of Eval in R}

\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
}

\maketitle

\begin{abstract}
This document is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
or Math in Paper Title or Abstract.
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Introduction}
- Why eval is used in R
- What the community says about using eval
- What existing tools do about eval
- Do people use eval for obvious things like looking up variable, if yes, it is
because they are unaware of alternatives?
- Why automating the transformation is a hard problem.
- What is the goal of the work? To replace eval with code for static analyssi or
for consumption by the users of the language?
- We only permit transformations that preserve code behavior?
- Do we accept overly complex code as the output?

@@

\section{Background on R}
- Talk about environments
- How is it different from JS (takes language, env in R but string in JS).

>>>>

\documentclass[conference]{IEEEtran}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\newcommand{\missingNumber}{\textcolor{red}{XX}\xspace}
\newcommand{\missingPercentage}{\textcolor{red}{XX\%}\xspace}
\newcommand{\missingTable}{\textcolor{red}{XXTable}\xspace}
\newcommand{\missingGraph}{\textcolor{red}{XXGraph}\xspace}
\usepackage{xcolor,xspace}
\begin{document}

\title{A Study of the Usage of Eval in R}

\author{\IEEEauthorblockN{For double blind review}%
  %\IEEEauthorblockA{ dept} \\ \and
}  
\maketitle

\renewcommand{\c}[1]{{\small\sf{#1}}\xspace}

\begin{abstract}

\end{abstract}

\section{Introduction}

The \c{eval} function has a bad reputation. This function, under one name or
another and with various exact semantics, is available in many dynamic
languages. It is used to transform text into code and execute that code.

- Why eval is used in R
- What the community says about using eval
- What existing tools do about eval
- Do people use eval for obvious things like looking up variable, if yes, it is
because they are unaware of alternatives?
- Why automating the transformation is a hard problem.
- What is the goal of the work? To replace eval with code for static analyssi or
for consumption by the users of the language?
- We only permit transformations that preserve code behavior?
- Do we accept overly complex code as the output?

@@

\section{Related Work}

\section{Eval in R}
- Talk about environments
- How is it different from JS (takes language, env in R but string in JS).
